Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-07-14 prop_letter.tex
Updating by Gerardo...

A key aspect of a quantum measurement is its statistical nature, as reflected
in the application of the Born rule to determine the probability of a given measurement 
outcome \nb\citep{Born1983,peres1995quantum,544199}. The Gleason
theorem establishes that there is no alternative to the Born rule by 
demonstrating, using reasonable continuity arguments in Hilbert spaces
of dimension $d\ge3$, the existence of a unique state 
$\rho$ consistent with the statistical predictions computed from 
that rule \nb\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
It is then legitimate to question what happens when infinite precision
cannot be achieved. We will show that, 
while a QIVPM  might not be consistent
with a unique state\nb$\rho$ on all projectors defined on a Hilbert space of dimension $d\ge3$,
if the QIVPM is induced by some mixed state\nb$\rho'$ ,

$\rho'$ would
close to $\rho$ when we shrink the length of intervals under some
good conditions, and recover the original Gleason theorem in the limiting
case.

>>>>

A key aspect of a quantum measurement is its statistical nature, as reflected
by application of the Born rule to determine the probability of a given measurement 
outcome \nb\citep{Born1983,peres1995quantum,544199}. The Gleason
theorem establishes that there is no alternative to the Born rule by 
demonstrating, using reasonable continuity arguments in Hilbert spaces
of dimension $d\ge3$, the existence of a unique state 
$\rho$ consistent with the statistical predictions computed from 
that rule \nb\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
It is then legitimate to question what happens when infinite precision
cannot be achieved. We will show that, if the effect of finite precision is incorporated, 
while a QIVPM  might not be consistent
with a unique state\nb$\rho$ on all projectors defined on a Hilbert space of dimension $d\ge3$, 
there is a mathematically precise sense in which one recovers the original Gleason theorem asymptotically. 
Specifically, if for bounded resources the QIVPM is induced by some mixed states \nb$\rho'$, 
those states will converge to a unique state $\rho$ when the size of the intervals characterizing 
the uncertainties tends to zero.
